---
title: 'Class 10: Web Scraping'
author: "Fadel M Megahed"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    code_download: true
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Robotstxt

The code chunk below will show the output from the [robotstxt package](https://github.com/ropensci/robotstxt) for the ISA course bulletin available at: <https://bulletin.miamioh.edu/courses-instruction/isa/index.html>


```{r robotstxt}
robotstxt::paths_allowed(paths = "/courses-instruction/isa/", domain = "bulletin.miamioh.edu", bot = "*")
```


## `robotstxt` demo: wikipedia

From the chunk below, we are allowed to scrape the [MU Football Wiki page](https://en.wikipedia.org/wiki/Miami_RedHawks_football).

```{r wiki}
robotstxt::paths_allowed(paths = "wiki/", domain = "https://en.wikipedia.org")
```

## `robotstxt` demo: LinkedIn 

From the example below, the `robotstxt` response is inconsistent with what the webpage says and is incorrect. As a general bot, we are not allowed to scrape anything from linkedIn.

```{r linkedin}
robotstxt::paths_allowed(paths = "jobs/", domain = "https://www.linkedin.com", bot ="*")
```

**If you removed the slash after the `.com`, the warning disappeared and we got a consistent result with the <https://www.linkedin.com/robots.txt> page.**


## `rvest` demo: ISA course bulletin

```{r rvest_demo}
isa_page_in_r = rvest::read_html("https://bulletin.miamioh.edu/courses-instruction/isa/")

# extract the titles
# if all titles look the same on the page, it means that they have the same tag/class, which would allow you to extract them in one step
# we got the selector below by:
## [a] highlighted the course
## [b] right clicked and selected inspect
## [c] found the part that was flushed containing the title
## [d] right clicked and copied the selector
## [e] I saw that the output from the code below just got me the 24th course so I dropped the `:nth-child(24)`
isa_page_in_r |> 
  rvest::html_elements(
    "#sc_sccoursedescs > div > p.courseblocktitle > strong"
  ) |> 
  rvest::html_text2() -> isa_titles

# course descriptions
# css selector obtained using the selector gadget
isa_page_in_r |>
  rvest::html_elements(".courseblockdesc")  |> 
  rvest::html_text2() -> isa_descs

isa_df = data.frame(
  title = isa_titles, description = isa_descs
)
```





